\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-23 pldi/draft.tex
Update eager fig
NOAA Pash results in paper

\begin{figure}[t]
\centering
% https://docs.google.com/drawings/d/13Zx3a9bWi1RvpOgNCSiXirp9UOte-XuaJQBi_lmmPMc/edit
\includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_eager.pdf}}
\caption{
  \textbf{Eager primitive.}
  Addressing intermediary laziness is challenging:
    (i) FIFOs are blocking;
    (ii) files alone introduce race conditions between producer/consumer;
    (iii) files \ttt{wait} inhibit task-based parallelism.
Eager \ttt{relay} nodes address the challenge while remaining within the \sys model.
% Describe. \TODO{Combine this figure with the above code maybe.}
}
\vspace{-15pt}
\label{fig:eager}
\end{figure}

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{\detokenize{./figs/tiling_throughput_scaleup.pdf}}
    \caption{
      \textbf{Speedup achieved by \sys as a function of the level of parallelism (1--100).} 
      Four different configurations per benchmark:
      (i) \todo{Par + Split}, showing the performance of \sys with both eager and split optimizations enabled,
      (ii) \todo{Par + B. Split}, showing the performance of \sys with eager and the \todo{batch-size annotated} split optimizations enabled,
      (iii) \todo{Parallel}, showing the performance of \sys with eager enabled and split disabled,
      (iv) \todo{No Eager}, showing the performance of \sys with split and eager disabled,
      (v) \todo{Blocking Eager}, showing the performance of \sys with split disabled and the naive blocking eager enabled,
      (vi) \todo{Opt. Parallel}, showing the performance of an optimized version of \ttt{bigrams}.
      \nv{Maybe it makes sense to show log x-axis?}
      \kk{How can we also fit two more plots (sort-sort and diff) here? Maybe we can fit one by getting rid of sort (since it also shown in the sort--parallel one). Otherwise we could separate the ``split'' plots from the ones that don't have split.}
    }
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

@@

\heading{Results}
The original pipeline executes in \todo{XXs} on \todo{XX}GB of input data.
Applying \sys with \todo{XX}$\times$ parallelism leads to (XX speedup).
Naturally, different phases benefit differently from parallelization: \todo{part 1, 2, 3, 4}

@@

In terms of program size, the Hadoop program amounts to 137 Java LoC as opposed to \todo{XX} shell LoC for \sys's \todo{part 4}.

@@

>>>>

\begin{figure}[t]
\centering
% https://docs.google.com/drawings/d/13Zx3a9bWi1RvpOgNCSiXirp9UOte-XuaJQBi_lmmPMc/edit
\includegraphics[width=0.48\textwidth]{\detokenize{./figs/dish_eager.pdf}}
\caption{
  \textbf{Eager primitive.}
  Addressing intermediary laziness is challenging:
    (i) FIFOs are blocking;
    (ii) files alone introduce race conditions between producer/consumer;
    (iii) files \ttt{wait} inhibit task-based parallelism.
Eager \ttt{relay} nodes address the challenge while remaining within the \sys model.
% Describe. \TODO{Combine this figure with the above code maybe.}
}
\vspace{-15pt}
\label{fig:eager}
\end{figure}

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{\detokenize{./figs/tiling_throughput_scaleup.pdf}}
    \caption{
      \textbf{Speedup achieved by \sys as a function of the level of parallelism (1--100).} 
      Four different configurations per benchmark:
      (i) \todo{Par + Split}, showing the performance of \sys with both eager and split optimizations enabled,
      (ii) \todo{Par + B. Split}, showing the performance of \sys with eager and the \todo{batch-size annotated} split optimizations enabled,
      (iii) \todo{Parallel}, showing the performance of \sys with eager enabled and split disabled,
      (iv) \todo{No Eager}, showing the performance of \sys with split and eager disabled,
      (v) \todo{Blocking Eager}, showing the performance of \sys with split disabled and the naive blocking eager enabled,
      (vi) \todo{Opt. Parallel}, showing the performance of an optimized version of \ttt{bigrams}.
      \nv{Maybe it makes sense to show log x-axis?}
    }
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

@@

\heading{Results}
The complete
%% original
shell pipeline executes in 44m2s for five years of weather data (which
amounts to 82GB).  Applying \sys with 2/10$\times$ parallelism leads
to (1.86/2.44$\times$ speedup).  Naturally, different phases benefit
differently from parallelization: downloading, extracting, and
preparing data benefits from 1.77/1.99$\times$ speedup (compared to
original 33m58s), while computing the maximum temperature benefits
from 2.30/10.79$\times$ speedup (original 10m4s). \todo{For an
  explanation of why speedup is more than the amount of parallelism}
  see Discussion-\sx{ours}.

@@

In terms of program size, the Hadoop program amounts to 137 Java LoC as opposed to a pipeline of \todo{5} shell commands for the same computation.

@@

\kk{Should we mention that we serve the weather data in the local network}
